% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Brian C. Smith}
\address{10106 Summit Avenue, Kensington, MD 20895}
\address{(301) 651-2656 | c.smith.brian@gmail.com}

% \address used twice to have two lines of address
 
\begin{resume}
 

 
 
\section{EDUCATION} 
  	{\sl Bachelor of Arts,} Philosophy \& Psychology \hfill 2008-2012 \\ 
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                St. Olaf College, Northfield, MN \\
                
 \section{WORK\\EXPERIENCE}                
                {\sl Kitchen Assistant} \hfill        Summers 2006-2008 \\
                Camp Pemigewassett, Wentworth, NH
                  \begin{itemize}
                   \item Cooked, prepared food, trained employees, inventoried, and cleaned. 
                   \end{itemize} 
                 
                 {\sl Cook} \hfill        Summer 2011 \\
                Clyde's of Chevy Chase, Washington, DC
                  \begin{itemize}
                   \item Managed outdoor barbecue service including food preparation and service. 
                   \end{itemize} 

				{\sl Driver} \hfill        July 2012-Present \\
                Takeout Taxi/Brenco Enterprises, Kensington, MD
                  \begin{itemize}
                   \item Pick up and deliver food from restaurants to customers. 
                   \end{itemize} 
                   
 \section{PROJECT\\EXPERIENCE} {\sl Researcher} \hfill 2010-2012 \\
                Psychology Department, St. Olaf College
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Designed experiments and conducted research for four long-term projects between 2010 and 2012.
                 \item Worked in teams and individually to design research, create measures and assessments, conduct research, and analyze results. 		
               
                \end{itemize}
                
                {\sl Research Programmer} \hfill            2010-2012 \\
                Psychology Department, St. Olaf College 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Analyzed various statistical data for above projects through computer software, particularly SPSS. 
                 \end{itemize} 

                {\sl Research Programmer} \hfill           Spring 2010 \\
                Statistics Department, St. Olaf College 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Collected and compiled labor and inflation statistics, analyzed data for further statistical research. 
                 \end{itemize}  
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} SPSS, R, Endnote, LaTeX, Minitab\\
                {\sl Operating Systems:} Windows, Mac, Linux.
\section{RELEVANT \\ COURSEWORK} Statistics for Science, Research Methods, Biopsychology, Formal Logic, Conditioning and Learning, History and Methods, Mind \& Body Research, Statistics, Health Psychology, Psychology of Personality
\section{EXTRA-\\CURRICULAR \\ ACTIVITIES} {\sl Member:} Philosophy Forum \hfill 2010-2012\\
{\sl Discussion Leader:} Philosophy Forum \hfill 2012\\
{\sl Member:} Eight Intramural Sports \hfill 2008-2012\\
{\sl Captain:} Three Seasons Intramural Soccer \hfill 2008-2011\\
\end{resume}
\end{document}
